\LARGE \bf WORKING TITLE: Incorporating User Feedback in Motion Planning for Manipulators

### 2014-09-29 paper2015asml.tex
background

Human motions have been the subject of recent stufy with the intent of determining whether there are certain motor or locomotor invariants that best describe human manipulation or locomotion. Human motion has been observed to be stereo-typical~\cite{Atkeson:85}, i.e. learned motion patterns that are repeatedly used. This requires less planning of individual motions and contributes to making human motions more deterministic and predictable. Human motion has also been found to be optimized Nyga et. al.~\cite{Nyga:2011} studied the reaching motions of several subjects in table-setting situations.

>>>>

Human motions have been the subject of recent stufy with the intent of determining whether there are certain motor or locomotor invariants that best describe human manipulation or locomotion. Human motion has been observed to be stereo-typical~\cite{Atkeson:85}, i.e. learned motion patterns that are repeatedly used. This requires less planning of individual motions and contributes to making human motions more deterministic and predictable. The minimum jerk principle for human motions specifies that the trajectory of the human can best be represented as a motion that minimizes jerk of the hand~\cite{Flash:85}. Uno et. al.~\cite{Uno:89} used minimum torque change as a measure to explain the observed human motions. Minimizing jerk at the joint level~\cite{Rosenbaum:1996} has been another criterion used for human motion. Human motion has also been found to be optimized~\cite{Arechavaleta:2006}. Albrech et. al.~\cite{Albrecht:2011} studied the reaching motions of several subjects in table-setting situations and attempted to codify the motion using cost functions representing minimum-jerk hand motions, minimum-jerk joint motions, minimum torque change and a combination of all three. They found that no single combination of the cost functions explained the observed data completely.

Recent work has also addressed the task of making motions predictable (similar motions in similar environments and tasks) and/or legible (make it easier for human observers to understand the intent of the robot)~\cite{Beetz:2010}. Legibility makes it possible for human observers to understand clearly what a robot is intending to do, allowing them to modify their actions and motions if necessary. Predictability implies that the robot will always be consistent in its actions, removing the element of surprise for human observers. These concepts have been well-studies recently with the intent of measuring legibility~\cite{Lichtenthaler:2011}, using expressions to improve the readability of robots~\cite{Takayama:2011} and generating anticipation~\cite{Gielniak:2011}. In~\cite{Dragan:2013}, the notion of legibility was incorporated into a constrained trajectory optimization motion planner to generate motions that are more legible to human observers.

There has been relatively little examination of how human observers perceive robot arm trajectories in environments with obstacles. There is no data available for how human observers react to such robot motions. It is not clear whether minimum-jerk trajectories (or other cost functions) are the best descriptors of motions in such environments or if there are other features that better explain human-observer preferences in such sitations. Our goal in this work is to collect the data needed to answer the query, "Which robot trajectories in cluttered environments do human-observers prefer". A second question that we would like to answer is "Why are certain robot trajectories preferred by human-observers?". This is a larger question that we aim to address in future work and instead we focus on,"Can we predict a human-observer preference for a given trajectory". The answer to this latter question, we hope, will eventually point us towards a cost function for generating more human friendly motion plans.
